The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-12-20 paper/main.tex
paper: correcting typos

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
This study develops simplified models of signal-to-noise limited transit 
surveys, in order to clarify the biases that stellar binarity introduces
to occurrence rate measurements.
Particular attention is paid to dilution of observed planet radii, errors in 
star counts, and treatment of detection efficiencies.
Given a somewhat restrictive set of assumptions, we derive a general formula 
for the apparent rate density, for which the free parameters include the true 
radius distribution of planets, and also the relative numbers of planets 
orbiting secondaries, primaries, and single stars.
From this formalism, we suggest that for most of the observed radius 
distribution (apparent planet radii $>2r_\oplus$), ignoring binarity only 
leads to errors in inferred occurrence rates at the $\lesssim 10\%$ level.
One corollary is that binarity seems unlikely to strongly influence the HJ 
rate discrepancy.
The errors created by ignoring binarity at smaller apparent radii might be 
larger: for instance, the absolute occurrence of Earth-sized planets could be 
overestimated by up to $\approx 50\%$.
A final point is that our formalism provides a quantitative argument for why
whenever high-resolution imaging follow-up discovers stellar neighbors of 
detected planets, the planet is more likely to orbit primary. 
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

A group of binarity-ignoring astronomers wants to measure the mean number of 
planets of a certain type per star of a certain type.
They perform a wide-field photometric search for planets that transit, and 
discover all for which
\begin{equation}
\left(\frac{{\rm S}}{{\rm N}}\right)
= ({\rm const}) \cdot \delta_{\rm obs} L_{\rm sys}^{1/2} d^{-1}
> \left(\frac{{\rm S}}{{\rm N}}\right)_{\rm floor}.
\label{eq:S_N_thresh}
\end{equation}
The observed transit depth $\delta_{\rm obs}$ constitutes the signal, ${\rm 
S}$. The survey is shot-noise dominated, and the fractional photon noise 
${\rm N}$ scales as the inverse root of the photon flux received from any 
stellar system, ${\rm N} \propto (L_{\rm sys}/d^2)^{-1/2}$, for $L_{\rm sys}$ 
the system luminosity and $d$ its distance.
The solid angle coverage, telescope area, and survey duration are part of the 
``const'' term of Eq.~\ref{eq:S_N_thresh}. The transit duration also 
affects detectability, but we omit it in this work for brevity.

@@

Outside of astrophysical differences, every term in 
Eq.~\ref{eq:defn_apparent_rate_density} is observationally-biased.
There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to misclassification of 
both planet radii and stellar properties.
There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because an apparently 
searchable point on the sky might include two searchable stars.
There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
have different masses and radii than assumed in the single-star case.
Binarity might also affect the observers' ability to correctly select 
searchable stars (but see Sec.~\ref{sec:discussion} for discussion of this 
issue).

@@

To gain intuition for the many observational biases at play,
we consider a set of idealized transit surveys.
First, we discuss the simplest possible cases (Sec.~\ref{sec:simplest}), in 
which all planets have identical properties, and all stars have identical 
properties except that some are in binaries.
The straightforward thought-experiments of Sec.~\ref{sec:simplest} are then 
generalized in Sec.~\ref{sec:general_formula} to allow for varying populations 
of secondaries, and for varying intrinsic occurrence rate distributions.
Sec.~\ref{sec:more_complicated} investigates questions of interest, 
including (a) measurements of $\eta_\oplus$, (b) the ``hot Jupiter rate 
discrepancy'', and (c) \citet{fulton_california-_2017}'s 
recently discovered ``valley''.
We discuss what our models suggest about binarity's biasing effects in 
Sec.~\ref{sec:discussion}, and conclude in Sec.~\ref{sec:conclusion}.

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{
        Cartoon of the searchable volumes for single stars ({\it left}), and 
        twin binaries ({\it right}).
        This model assumes all stars have equal mass and luminosity, and 
        all planets have the same true radius $r=r\p$.
        {\it Top:} At an apparent radius $r\a=r\p$,
        the observer searched twin binaries out to a larger         
        distance, $\sqrt{2}\times$ that of single stars.
        Because of dilution, there are no planets in twin binaries with 
        $r\a=r\p$.
        {\it Middle:} At an apparent radius $r\a=r\p/\sqrt{2}$, the 
        searched volumes are half those at $r\a=r\p$. 
        The only detected planets with $r\a=r\p/\sqrt{2}$ orbit twin binaries.
        {\it Bottom:} Planets with a true radius $r=r\p$ are searchable to 
        a maximum distance $d_0$ around singles, and $d_0/\sqrt{2}$ around 
        twin binaries.
    }
    \label{fig:model_1_volumes}
\end{figure}

@@

First, what are the possible apparent radii of detected planets?
If the true planet radius is $r=r\p$, then planets in singles will be 
detected with the identical apparent radii: $r\a = r\p$.
Conversely, all detections in twin binaries will have apparent radii 
$r\a=r\p/\sqrt{2}$, because they are diluted.
For an unresolved point-source,
\begin{equation}
\delta_{\rm obs}
= \left(\frac{r\a}{R\a}\right)^2
= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
        sys}(M_1, q)},
\label{eq:delta_obs_general} 
\end{equation}
where $R_{\rm host}$ ($L_{\rm host}$) is the planet-host's stellar radius 
(luminosity), $R\a$ is the apparent stellar radius, $L_{\rm sys}=L_1+L_2 = 
L(M_1) + L(qM_1)$ is the system luminosity, and $q=M_2/M_1$ is the binary mass 
ratio.
We assume that the stellar radius and luminosity are uniquely related to the 
stellar mass.
The observers, with no a priori knowledge of the distance to a system, would 
measure a flux, assume a stellar mass $M\a=M_1$, and estimate both a stellar 
radius $R\a = R(M\a)$ and an under-luminous system luminosity of $L_{\rm 
sys,a}(M\a) = L(M\a)$.

@@

We can write similar equations for the binaries.
First though, we define a ratio $\mu \equiv N\s^{\rm b}(r\a) / N\s^0(r\a)$ 
between the number of searchable binary systems and the number of searchable 
singles at a given $r\a$.
This quantity is useful because although $N\s^{\rm b}$ and $N\s^0$ vary
as a function of the observed transit depth, $\mu$ remains fixed.
Applying this definition, at $r\a=r\p/\sqrt{2}$, some detections will come 
from primaries,
\begin{equation}
n_{\rm det}^1(r\a) =
\mu N\s^0(r\a) Z_1 p_{\rm tra}
\cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
\end{equation}
and some from secondaries,
\begin{equation}
n_{\rm det}^2(r\a) = 
\mu N\s^0(r\a) Z_2 p_{\rm tra}
\cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
\end{equation}
where $Z_1$ is the number of planets per primary, $Z_2$ is the number of 
planets per secondary, and $p_{\rm tra}$ is the same for identical stars.
In the case of twin binaries, Eq.~\ref{eq:N_searchable_prop} gives $\mu = 
2^{3/2} n_{\rm b}/n_{\rm s} = 2^{3/2} {\rm BF}/(1-{\rm BF})$, for ${\rm BF}$ 
the binary fraction\footnote{The binary fraction is the fraction of systems in 
a volume-limited sample that are binary. It is equivalent to the multiplicity 
fraction if there are no triple, quadruple, or higher order multiples.
}.

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
        radius, for a model with identical stars, identical planets, and twin 
        binaries.
        We assume a twin binary fraction of ${\rm BF}=0.1$, and that all 
        stars (single, primary, and secondary) host planets at equal 
        rates.
        If the true planet radius is $r\p$, all planets detected in binaries 
        will have apparent radii $r\a = r\p/\sqrt{2}$ (see 
        Eq.~\ref{eq:model_1_apparent_rate_density}).
        The rate and rate density are related by $\Lambda|_a^b = 
        \int_{a}^{b}\Gamma\,{\rm d}r$.
    }
    \label{fig:occ_rate_model_1}
\end{figure}

@@

A simple extension to the previous example will help us further distinguish 
the detected populations.
Consider now a universe that is the same in every respect to that of 
Sec.~\ref{sec:model_1}, except now half of planets have radii $r\p$, while 
the other half have $r\p/\sqrt{2}$.
The true rate densities are
\begin{equation}
\Gamma_i(r) = \frac{Z_i}{2} \left[
\delta(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
\right], \quad {\rm for}\  i \in \{ 0,1,2 \},
\end{equation}
where as always $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
secondaries, and the $Z_i$'s are the number of planets per star of each type.

Following an identical line of reasoning as before, the apparent rate density 
can be written
\begin{align}
\notag
\Gamma\a(r\a) &=
\frac{1}{2(1+\mu)} \left[
Z_0 \cdot \delta(r\a - r\p)
+
\left[Z_0 + \mu (Z_1 + Z_2)
\right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad+
\left.
\mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
\right].
\label{eq:two_radii_twins}
\end{align}
The important qualitative point of this equation is that at $r\a = 
r\p/\sqrt{2}$, two populations contribute.
The first population is singles with $r=r\p/\sqrt{2}$, and the second is twin 
binaries with $r=r\p$.
Both populations are detected out to the same maximum searchable distance.
Just as with Eq.~\ref{eq:apparentlysearchable_to_searchable}, we will have a 
cancellation of $N\s^0(r\a)$ terms, leaving only the $\mu$ weights.

@@

To generalize the procedure of Sec.~\ref{sec:simplest}, we consider a SNR 
limited transit survey in which all the primaries and single stars have 
identical properties.
For example, they might all be solar analogs, roughly similar to 
the stars that {\it Kepler} surveyed~\citep{batalha_selection_2010}.
We let the properties of the secondaries vary, and assume that there are some 
functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
terms of its mass.
We then allow for an arbitrary volume-limited mass ratio distribution 
$f(q)$, and also for arbitrary true rate densities for singles, primaries, 
and doubles ($\Gamma_0, \Gamma_1, \Gamma_2$).
Since the properties of the secondaries vary, we must consider not only the 
dependence of the rate densities on planet radius, but also on stellar mass.
We presume that the observers always take the properties of a binary system to 
be those of the primary.

@@

\paragraph{Ratio of searchable binaries to singles}
We must also specify the exact form of $\mu({\rm BF},M\a)$, the ratio of 
the number of searchable binary systems to singles.
Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
recall that the maximum searchable distance for singles and binaries are 
proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
Applying Eq.~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
\frac{N\s^{\rm b}(r_a)}{N_s^0(r\a)}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\mathrm{d}q.
\label{eq:mu_general}
\end{equation}

If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this reduces to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
\label{eq:mu_power_laws}
\end{equation}
which may be written in a closed form using the hypergeometric function.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform, qualitatively similar to {\it e.g.}, 
        \citet{raghavan_survey_2010}'s Fig.~16.
        At a given observed depth, the searchable binaries in a transit survey 
        are magnitude-limited.
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}

@@

\section{More complicated transit survey models}
\label{sec:more_complicated}
The following section applies our general equation for the apparent rate 
density (Eq.~\ref{eq:general_Gamma_a}) to study binarity's effects in more 
realistic regimes.
In general, we will write the rate density for each type of star, 
$\Gamma_i(r)$, as the product of a shape function and a constant:
\begin{equation}
\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i f_i(r),
\quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where as awlays, $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
The shape function is normalized to unity.
The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
over all planetary radii. In other words, they are number of planets per 
single, primary, or secondary star.
This section will consider the effects of varying both $f_i(r)$ and also the
relative values of the $Z_i$'s.

@@

This study presented simple models for the effects of binarity on occurrence 
rates measured by transit surveys.
The simplest of these models (Sec.~\ref{sec:simplest}) provided an 
order-of-magnitude estimate for how much binarity might affect occurrence 
rates: by no more than $\sim$factors of two.

We then gave a general formula for the apparent rate density inferred by an 
observer ignoring binarity (Eq.~\ref{eq:general_Gamma_a}).
As input, this equation requires a volume-limited mass ratio distribution 
$f(q)$, and also the true rate densities for planets around singles, 
primaries, and secondaries.
The assumptions that make the model tractable are:
\begin{enumerate}
    \item the transit survey is SNR limited;
    \item all the primaries and single stars have identical properties;
    \item the properties of the secondaries can vary, but there are known 
    functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
    terms of its mass;
    \item the binarity-ignoring observers assume that binaries have the same 
    properties as the primaries.
\end{enumerate}

Allowing for these conditions, many results follow:
\begin{itemize}
%
\item Assuming a power-law planet radius distribution, and that the same 
number of planets orbit singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level from radii $2r_\oplus \lesssim r\a \lesssim 
17r_\oplus$ (Sec.~\ref{sec:model_2}).
%
\item Assuming a broken-power law planet radius distribution, with 
\citet{howard_planet_2012}'s exponent at $r > 2r_\oplus$ and a constant 
occurrence at $r < 2r_\oplus$, there is a ``bump'' in the apparent rate 
density at $r\a < 2r_\oplus$, leading to a relative error $\delta \Gamma_0 = 
|\Gamma_0 - \Gamma\a|/\Gamma_0$ of at most $\approx 50\%$ 
(Fig.~\ref{fig:occ_rate_model_3_log}).
Although this is smaller than current systematic uncertainties on the 
occurrence rates of Earth-sized planets, this means that binarity could
eventually become an important component of the $\eta_\oplus$ error budget.
%
\item Binarity ``fills in'' gaps in the radius distribution 
(Fig.~\ref{fig:model_4}), by an amount that could affect precise measurements 
of the depth, width, and slope of \citet{fulton_california-_2017}'s radius 
gap, in the event that planets are not carefully vetted with high resolution 
imaging.
This will likely become an important consideration for precise measurements of 
the depth, width, and slope of .
%
\item Binarity does not lead to smaller apparent HJ occurrence rates 
(Fig.~\ref{fig:gaussian_HJ}).
This assumes a Gaussian planet radius distribution, similar to that reported 
by~\citet{petigura_CKS_2017}.
\end{itemize}

>>>>

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
This study develops simplified models of signal-to-noise limited transit 
surveys, in order to clarify the biases that stellar binarity introduces
to occurrence rate measurements.
Particular attention is paid to dilution of observed planet radii, errors in 
star counts, and treatment of detection efficiencies.
Given a somewhat restrictive set of assumptions, we derive a general formula 
for the apparent rate density, for which the free parameters include the true 
planet radius distribution, and also the relative numbers of planets 
orbiting secondaries, primaries, and single stars.
From this formalism, we suggest that for most of the observed radius 
distribution (apparent planet radii $>2r_\oplus$), ignoring binarity only 
leads to errors in inferred occurrence rates at the $\lesssim 10\%$ level.
One corollary is that binarity seems unlikely to strongly influence the HJ 
rate discrepancy.
The errors created by ignoring binarity at smaller apparent radii might be 
larger: for instance, the absolute occurrence of Earth-sized planets could be 
overestimated by up to $\approx 50\%$.
A final point is that our formalism provides a quantitative argument for why
whenever high-resolution imaging follow-up discovers stellar neighbors of 
detected planets, the planet is more likely to orbit the primary. 
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

A group of binarity-ignoring astronomers wants to measure the mean number of 
planets of a certain type per star of a certain type.
They perform a wide-field photometric search for planets that transit, and 
discover all for which
\begin{equation}
\left(\frac{{\rm S}}{{\rm N}}\right)
= ({\rm const}) \cdot \delta_{\rm obs} L_{\rm sys}^{1/2} d^{-1}
> \left(\frac{{\rm S}}{{\rm N}}\right)_{\rm floor}.
\label{eq:S_N_thresh}
\end{equation}
The observed transit depth per unit stellar flux $\delta_{\rm obs}$ 
constitutes the signal, ${\rm S}$.
The survey is shot-noise dominated, and the fractional photon noise 
${\rm N}$ scales as the inverse root of the photon flux received from any 
stellar system, ${\rm N} \propto (L_{\rm sys}/d^2)^{-1/2}$, for $L_{\rm sys}$ 
the system luminosity and $d$ its distance.
The solid angle coverage, telescope area, and survey duration are part of the 
``const'' term of Eq.~\ref{eq:S_N_thresh}. The transit duration also 
affects detectability, but we omit it in this work for brevity.

@@

Outside of astrophysical differences, every term in 
Eq.~\ref{eq:defn_apparent_rate_density} is observationally-biased.
There are errors in $n_{\rm det}(\pp\a,\ps\a)$ due to misclassification of 
both planet radii and stellar properties.
There are errors in $N_{{\rm s,a}}(\pp\a,\ps\a)$ because a 
searchable point on the sky might be two searchable stars.
There are errors in $p_{\rm tra}(\pp\a,\ps\a)$ because stars in binaries may 
have different masses and radii than assumed in the single-star case.
Binarity might also affect the observers' ability to correctly select 
searchable stars (but see Sec.~\ref{sec:discussion} for discussion of this 
issue).

@@

To gain intuition for the many observational biases at play,
we consider a set of idealized transit surveys.
First, we discuss the simplest possible cases (Sec.~\ref{sec:simplest}), in 
which all planets have identical properties, and all stars have identical 
properties except that some are in binary systems.
The straightforward thought-experiments of Sec.~\ref{sec:simplest} are then 
generalized in Sec.~\ref{sec:general_formula} to allow for varying populations 
of secondaries, and for varying intrinsic occurrence rate distributions.
Sec.~\ref{sec:more_complicated} investigates questions of interest, 
including (a) measurements of $\eta_\oplus$, (b) the ``hot Jupiter rate 
discrepancy'', and (c) \citet{fulton_california-_2017}'s 
recently discovered ``valley''.
We discuss what our models suggest about binarity's biasing effects in 
Sec.~\ref{sec:discussion}, and conclude in Sec.~\ref{sec:conclusion}.

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{
        Cartoon of the searchable volumes for single stars ({\it left}), and 
        twin binaries ({\it right}).
        This model assumes all stars have equal mass and luminosity, and 
        all planets have the same true radius $r=r\p$.
        {\it Top:} At an apparent radius $r\a=r\p$,
        the observer searched twin binaries out to a
        distance $\sqrt{2}\times$ that of single stars.
        Because of dilution, there are no planets in twin binaries with 
        $r\a=r\p$.
        {\it Middle:} At an apparent radius $r\a=r\p/\sqrt{2}$, the 
        maximum searchable distances are half those at $r\a=r\p$. 
        The only detected planets with $r\a=r\p/\sqrt{2}$ orbit twin binaries.
        {\it Bottom:} Planets with a true radius $r=r\p$ are searchable to 
        a maximum distance $d_0$ around singles, and $d_0/\sqrt{2}$ around 
        twin binaries.
    }
    \label{fig:model_1_volumes}
\end{figure}

@@

First, what are the possible apparent radii of detected planets?
If the true planet radius is $r=r\p$, then planets in singles will be 
detected with identical apparent radii: $r\a = r\p$.
Conversely, all detections in twin binaries will have apparent radii 
$r\a=r\p/\sqrt{2}$, because they are diluted.
For an unresolved point-source,
\begin{equation}
\delta_{\rm obs}
= \left(\frac{r\a}{R\a}\right)^2
= \left[{r\over R_{\rm host}}\right]^2\times {L_{\rm host} \over L_{\rm 
        sys}(M_1, q)},
\label{eq:delta_obs_general} 
\end{equation}
where $R_{\rm host}$ ($L_{\rm host}$) is the planet-host's stellar radius 
(luminosity), $R\a$ is the apparent stellar radius, $L_{\rm sys}=L_1+L_2 = 
L(M_1) + L(qM_1)$ is the system luminosity, and $q=M_2/M_1$ is the binary mass 
ratio.
We assume that the stellar radius and luminosity are uniquely related to the 
stellar mass.
The observers, with no a priori knowledge of the distance to a system, would 
measure a flux, assume a stellar mass $M\a=M_1$, and estimate both a stellar 
radius $R\a = R(M\a)$ and an under-luminous system luminosity of $L_{\rm 
sys,a}(M\a) = L(M\a)$.

@@

We can write similar equations for the binaries.
First though, we define a ratio $\mu \equiv N\s^{\rm b}(r\a) / N\s^0(r\a)$ 
between the number of searchable binary systems and the number of searchable 
singles at any $r\a$.
This quantity is useful because although $N\s^{\rm b}$ and $N\s^0$ vary
as a function of the observed transit depth, $\mu$ remains fixed.
Applying this definition, at $r\a=r\p/\sqrt{2}$, some detections will come 
from primaries,
\begin{equation}
n_{\rm det}^1(r\a) =
\mu N\s^0(r\a) Z_1 p_{\rm tra}
\cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
\end{equation}
and some from secondaries,
\begin{equation}
n_{\rm det}^2(r\a) = 
\mu N\s^0(r\a) Z_2 p_{\rm tra}
\cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right),
\end{equation}
where $Z_1$ is the number of planets per primary, $Z_2$ is the number of 
planets per secondary, and $p_{\rm tra}$ is the same for identical stars.
In the case of twin binaries, Eq.~\ref{eq:N_searchable_prop} gives $\mu = 
2^{3/2} n_{\rm b}/n_{\rm s} = 2^{3/2} {\rm BF}/(1-{\rm BF})$, for ${\rm BF}$ 
the binary fraction\footnote{The binary fraction is the fraction of systems in 
a volume-limited sample that are binary. It is equivalent to the multiplicity 
fraction if there are no triple, quadruple, or higher order multiples.
}.

@@

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred occurrence rates over $0.01r_\oplus$ bins in planet 
        radius, for a model with identical stars, identical planets, and twin 
        binaries (same as Fig.~\ref{fig:model_1_volumes}).
        We assume a twin binary fraction of ${\rm BF}=0.1$, and that all 
        stars (single, primary, and secondary) host planets at equal 
        rates.
        If the true planet radius is $r\p$, all planets detected in binaries 
        will have apparent radii $r\a = r\p/\sqrt{2}$;
        Eq.~\ref{eq:model_1_apparent_rate_density} gives the normalizations.
        The rate and rate density are related by $\Lambda|_a^b = 
        \int_{a}^{b}\Gamma\,{\rm d}r$.
    }
    \label{fig:occ_rate_model_1}
\end{figure}

@@

A simple extension to the previous example will help us further distinguish 
the detected populations.
Consider now a universe that is the same in every respect to that of 
Sec.~\ref{sec:model_1}, except that half of planets have radii $r\p$, while 
the other half have $r\p/\sqrt{2}$.
The true rate densities are
\begin{equation}
\Gamma_i(r) = \frac{Z_i}{2} \left[
\delta(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
\right], \quad {\rm for}\  i \in \{ 0,1,2 \},
\end{equation}
where as before $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
secondaries, and the $Z_i$'s are the number of planets per star of each type.

Following an identical line of reasoning as in Sec.~\ref{sec:model_1}, the 
apparent rate density can be written
\begin{align}
\notag
\Gamma\a(r\a) &=
\frac{1}{2(1+\mu)} \left[
Z_0 \cdot \delta(r\a - r\p)
+
\left[Z_0 + \mu (Z_1 + Z_2)
\right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad+
\left.
\mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
\right].
\label{eq:two_radii_twins}
\end{align}
The important qualitative point of this equation is that at $r\a = 
r\p/\sqrt{2}$, two populations contribute.
The first population is singles with $r=r\p/\sqrt{2}$, and the second is twin 
binaries with $r=r\p$.
Both populations are detected out to the same maximum searchable distance.
Just as with Eq.~\ref{eq:apparentlysearchable_to_searchable}, we will have a 
cancellation of $N\s^0(r\a)$ terms, leaving only the $\mu$ weights.

@@

To generalize the procedure of Sec.~\ref{sec:simplest}, we consider an SNR 
limited transit survey in which all the primaries and single stars have 
identical properties.
For example, they might all be solar analogs, roughly similar to 
the stars that {\it Kepler} surveyed~\citep{batalha_selection_2010}.
We let the properties of the secondaries vary, and assume that there are some 
functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
terms of its mass.
We then allow for an arbitrary volume-limited mass ratio distribution 
$f(q)$, and also for arbitrary true rate densities for singles, primaries, 
and doubles ($\Gamma_0, \Gamma_1, \Gamma_2$).
Since the properties of the secondaries vary, we must consider not only the 
dependence of the rate densities on planet radius, but also on stellar mass.
We presume that the observers always take the properties of a binary system to 
be those of the primary.

@@

\paragraph{Ratio of searchable binaries to singles}
We must also specify the exact form of $\mu({\rm BF},M\a)$, the ratio of 
the number of searchable binary systems to singles.
Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
recall that the maximum searchable distance for singles and binaries are 
proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
Applying Eq.~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
\frac{N\s^{\rm b}(r_a)}{N_s^0(r\a)}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\mathrm{d}q.
\label{eq:mu_general}
\end{equation}
If $\mathrm{BF}$ is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this reduces to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta\mathrm{d}q,
\label{eq:mu_power_laws}
\end{equation}
which may be written in a closed form using the hypergeometric function.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform, qualitatively similar to {\it e.g.}, 
        \citet{raghavan_survey_2010}'s Fig.~16.
        At a given observed transit depth, the searchable binaries in a 
        transit survey are magnitude-limited.
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}

@@

\section{More complicated transit survey models}
\label{sec:more_complicated}
The following section applies our general equation for the apparent rate 
density (Eq.~\ref{eq:general_Gamma_a}) to study binarity's effects in more 
realistic regimes.
In general, we will write the rate density for each type of star, 
$\Gamma_i(r)$, as the product of a shape function and a constant:
\begin{equation}
\Gamma_i(r) = \frac{{\rm d}\Lambda_i}{{\rm d}r} = Z_i f_i(r),
\quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where as always, $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
The shape function is normalized to unity.
The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
over all planetary radii. In other words, they are number of planets per 
single, primary, or secondary star.
This section will consider the effects of varying both $f_i(r)$ and also the
relative values of the $Z_i$'s.

@@

This study presented simple models for how binarity affects occurrence 
rates measured by transit surveys.
The simplest of these models (Sec.~\ref{sec:simplest}) provided an 
order-of-magnitude estimate that showed we would need very high twin binary 
fractions for binarity to affect apparent occurrence rates by more than 
$\sim$factors of two.

We then gave a general formula for the apparent rate density inferred by an 
observer ignoring binarity (Eq.~\ref{eq:general_Gamma_a}).
As input, this equation requires a volume-limited mass ratio distribution 
$f(q)$, and also the true rate densities for planets around singles, 
primaries, and secondaries.
The assumptions that make the model tractable are:
\begin{enumerate}
    \item the transit survey is SNR limited;
    \item all the primaries and single stars have identical properties;
    \item the properties of the secondaries can vary, but there are known 
    functions $L(M)$ and $R(M)$ that specify a star's luminosity and radius in 
    terms of its mass;
    \item the binarity-ignoring observers assume that binaries have the same 
    properties as the primaries.
\end{enumerate}
Allowing for these conditions, many results follow:
\begin{itemize}
%
\item Assuming a power-law planet radius distribution, and that the same 
number of planets orbit singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level from radii $2r_\oplus \lesssim r\a \lesssim 
17r_\oplus$ (Sec.~\ref{sec:model_2}).
%
\item Assuming a broken-power law planet radius distribution, with 
\citet{howard_planet_2012}'s exponent at $r > 2r_\oplus$ and a constant 
occurrence at $r < 2r_\oplus$, there is a ``bump'' in the apparent rate 
density at $r\a < 2r_\oplus$, leading to a relative error $\delta \Gamma_0 = 
|\Gamma_0 - \Gamma\a|/\Gamma_0$ of at most $\approx 50\%$ 
(Fig.~\ref{fig:occ_rate_model_3_log}).
Although this is smaller than current systematic uncertainties on the 
occurrence rates of Earth-sized planets, this means that binarity could
eventually become an important component of the $\eta_\oplus$ error budget.
%
\item Binarity ``fills in'' gaps in the radius distribution 
(Fig.~\ref{fig:model_4}), by an amount that could affect precise measurements 
of the depth, width, and slope of \citet{fulton_california-_2017}'s radius 
gap, in the event that planets are not carefully vetted with high resolution 
imaging.
%
\item Binarity does not lead to smaller apparent HJ occurrence rates 
(Fig.~\ref{fig:gaussian_HJ}).
This assumes a Gaussian planet radius distribution, similar to that reported 
by~\citet{petigura_CKS_2017}.
\end{itemize}
